Disk Winds Matter: Simulating the Optical Spectra of Cataclysmic Variables

### 2014-08-20 draft.tex
First draft to send round

\begin{document}
%% define bibstyle and other definitions
\bibliographystyle{aabib}
%% renew commands
\renewcommand{\labelitemi}{$\bullet$}
\def\py{\textsc{Python} }
\def\tar{\textsc{Tardis} }
\def\cld{\textsc{Cloudy} }
\def\civ{C~\textsc{iv} }
\def\araa{ARAA}
\def\nat{Nature}
\def\apjl{ApJ Letters}
\def\aapr{AAPR}
\def\ssr{SSR}
\def\apj{ApJ}
\def\pasp{PASP}
\def\aap{A\&A}
\def\mnras{MNRAS}
\def\aj{AJ}
\def\rmxaa{RMXAA}

@@

\begin{abstract}
High-State non-magnetic Cataclysmic Variables (CVs) 
exhibit strong Hydrogen \& Helium recombination lines in their optical 
spectra. These lines can be single peaked, and may be formed 
in the same bipolar outflow that is responsible for the
blue-shifted absorption lines seen in the Ultraviolet (UV).
Here we present results obtained by incorporating a `macro-atom' treatment into
our Monte Carlo radiative transfer code, which was
originally used to synthesize the UV spectrum of a disk-dominated CV 
with a simple biconical wind. Using an identical model, we show that the wind leaves a noticeable imprint 
on the optical spectrum, producing He II 4686 and H${\alpha}$ as well as
enhanced emission in the Ly-$\alpha$ and He II $1640$ UV lines. We find that 
a boundary layer is not essential to produce significant recombination to 
He II, and if one is present we favour temperatures of $<10^5$K to avoid
overionizing the UV resonance line species such as CIV. We also conduct Zanstra method
calculations and estimate that one would infer a boundary layer temperature of around 80,000K
from our benchmark model, which does not include one. This suggests that previous calculations
done using this method are strongly dependent on both the assumed geometry and disk
spectrum.
We also note that
the presence of a boundary layer becomes more noticeable in lower accretion rate systems.
In addition, the improved treatment of recombination means that the bound-free continuum
emission is enhanced, albeit by a modest amount.
A short exploration of a 3-variable kinematic parameter space leads to models with higher densities 
that are able to produce single-peaked line emission, and also generate sufficient recombination emission
to fill in the Balmer jump photoabsorption edge.
Finally, we present a synthetic spectrum of a next generation model in and out of eclipse,
and identify the strengths and shortcomings of the model in the context of the high inclination
Nova-like variable RW Tri.
\end{abstract}

@@

Figure~\ref{spec} shows optical synthetic spectra for the benchmark 
model for 5 different sightlines. The first thing to note is that the 
model produces some lines which are strong enough to overcome
the absorption cores lines from the disk. These lines are generally double peaked, 
implying they were formed near the base of the wind where rotational velocity
can still dominate over the slowly increasing poloidal velocity. A Balmer 
jump is present at all inclinations. This is present
in the stellar atmosphere models used to model the disk,
and is not a result of photoabsorption through the wind.
%%%% SAY BALMER JUMP CASUED BY SAs

In fact, the wind has a Balmer jump in emission, but it is not prominent enough
to overcome the intrinsic absorption in the illuminating spectrum. 
Figure~\ref{cont} shows the total escaping spectrum, integrated
over all viewing angles, with the contribution from the disk and wind
also plotted. It shows that the lines are produced in the wind,
and also that the wind is producing a Balmer recombination
continuum, but one which is not yet sufficient to mask the absorption 
intrinsic to the disk SED. This offers a tantalising hint
that modest changes to the kinematics of the wind
may be sufficient to boost the continuum emission of the wind.
Furthermore, it confirms our suspicions that the improved
radiative transfer would cause enhanced recombination emission,
suggesting that, where possible, up to date treatments of
NLTE line transfer should be used in codes such as this.
The prominent P-Cygni profiles in e.g., C\textsc{iv} are still seen
in the UV spectra (see figure~\ref{spec}). In addition, the wind 
now contributes significant Lyman-$\alpha$ and
He~\textsc{ii}~$\lambda1640{\rm \AA}$  emission. 
% We note that the ionization state of the wind 
% is such that recombination to He~\textsc{ii} is significant, even
% without a boundary layer as a source of higher energy photons.

@@

\begin{figure} 
\includegraphics[width=0.5\textwidth]{figures/fig4.eps}
\caption{Total packet-binned spectra across all viewing angles. The top panel shows the total 
integrated escaping spectrum, while the other panels show the contributions from photons that originate
in the disk and wind respectively. Recombination continuum emission blueward of the Balmer 
edge is already prominent relative to other wind continuum processes, but is not sufficient
to fill in the Balmer jump in this specific model}
\label{cont}
\end{figure}

@@

\noindent\rule{16cm}{0.4pt}

{\bf
\noindent key points here:

\begin{itemize}
	\item producing single peaked line profiles is difficult to say the least
	\item with our high density models we can produce some single peaked line emission,
	mostly in Halpha and beta. the other lines seem to stay double peaked.
	\item this higher density causes (too much) collisionally excited line emission from CIV
	\item if the wind was more equatorial then this might help, but this isn't really supported by observations.
	\item we can definitely reproduce the behaviour predicted by Murray and Chiang
	\item Comment on the observed Balmer decrement being fairly flat, as is observed. Point out that
	this is necessary if H alpha is to be single peaked, as you need significant optical depths.
	\item \la needs to be discussed somewhere- potentially here. Personally I would like to point out
	that recombination being important here suggests that it might also be in QSOs
\end{itemize}
}

\noindent\rule{16cm}{0.4pt}

Figure~\ref{halpha} shows how the H$\alpha$ and H$\beta$ lines change with the kinematics 
of the wind at an inclination of $80^\circ$. For H$\alpha$, in models with lower densities, the
line is double peaked, but we see a transition to a single peaked line when 
a high enough density is reach such that the line becomes optically thick.
This reproduces the behaviour predicted by \cite{MC96}, who suggested that
the poloidal velocity gradient in the wind can be larger than the gradient of 
the Keplerian velocity. This gradient can therefore modify the line profile shape.
It is clear from the behaviour of H$\beta$

In order to produce single-peaked line emission at high inclinations,
it is clear that a higher line opacity is needed at the red and blue wings relative to
the opacity at line centre. This can be achieved in a number of ways. A more equatorial 
wind would cause the line opacity at line centre to decrease
relative to the the wings of the line due to the increased radial component 
of the velocity gradient.

Our difficulty in producing single-peaked line emission from a full 
radiative transfer calculation has been encountered before. SDL05 found that a 
biconical disk geometry similar to that adopted here could not reproduce 
the observed single peaked profiles in YSOs.

\begin{figure} %fullpage
\mbox{
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_alpha_0.eps}}
\quad
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_beta_0.eps}}   
}
\caption{
% How the H$\alpha$ and H$\beta$ lines in our model change with the kinematic properties
% of the wind. The three separate panels show three different values of $\dot{M}_W$, 
% while $\alpha$ and $R_v$ are all gradually increased from top to bottom and left to right respectively.
% Larger values of these quantities increase the density at the base of the wind. There is a clear transition
% from double peaked to single peaked behaviour, and at the highest densities the wind
% essentially becomes neutral as the optically thick regions self-shield the wind from photoionizing radiation.
\bf{Each of these figures will highlight the next gen model in bold.
and contain a grid like the above showing a pair of spectral features in
the left and right panels. The grey shaded line will show the benchmark model
for easy comparison.  
The most promising parameters at the moment are acceleration exponent and launch radii.}
}
\label{halpha}
\end{figure} %fullpage

@@

\noindent\rule{16cm}{0.4pt}

{\bf
\noindent key points here:

\begin{itemize}
	\item there is always recombination continuum emission from the wind, but it
	only because significant w.r.t disk when the wind accelerates more slowly.
	\item This higher density causes (too much) collisionally excited line emission from CIV
	\item supports findings from the line profile shapes conclusions above...suggests
	we need to alter the geometry in some respect, or find someway to suppress
	collisionally excited line emission from UV lines?
	\item perhaps one should increase the volume of the emitting area rather than the density,
	although this will also cause more thermal line emission...
	\item Bottom lines: filling in the Balmer jump can be done, and at the very minimum recombination
	emission from the wind can matter, especially if we believe that the lines come from the wind. 
	But to properly fill in the edge, one requires very high, possibly unrealistic, densities.
	\item make clear that the edge originally comes from the stellar atmosphere, and that
	the model we have used here is perhaps a little pessimistic.
	\item We predict that the Balmer jump becomes deeper relative to the continuum 
	\item This is probably due to foreshortening of the disk continuum but a fairly constant
	escaping Balmer continuum.
\end{itemize}
}

\noindent\rule{16cm}{0.4pt}

\begin{figure} %fullpage
\mbox{
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_1640_0.eps}}
\quad
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_4686_0.eps}}   
}
%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
\caption{
The evolution of the He II lines with the kinematic properties
of the wind. 
% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
% when the wind becomes a neutral absorbing column.
}
\label{jump}
\end{figure}

@@

\noindent\rule{16cm}{0.4pt}

@@

{\bf 
\noindent key points here:

\begin{itemize}
	\item we don't necessarily need a Boundary layer to ionize Helium II
	\item a Boundary layer of 200,000K overionizes Carbon IV
	\item we therefore favour lower boundary layer temperatures, as supported
	by the upper limits of Hoare and Drew 1991.
	\item we expect a boundary layer to matter more in lower accretion
	rate systems.
\end{itemize}
}

\noindent\rule{16cm}{0.4pt}

@@

We introduce boundary layers with temperatures of 80,000K and 200,000K,
commonly proposed values in the literature. We find that a boundary layer

@@

Here f(line) is the line flux in erg~cm$^{-2}$ s$^{-1}$.

@@

\begin{figure} %fullpage
\mbox{
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_balmer_0.eps}}
\quad
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_uv_0.eps}}   
}
%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
\caption{The evolution of the Balmer jump and C~\textsc{iv} line with the kinematic properties
of the wind. 
% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
% when the wind becomes a neutral absorbing column.
}
\label{jump}
\end{figure}

@@

\newpage

@@

\begin{table}
\centering
\begin{tabular}{p{3cm}p{4cm}}
Model B \\
\hline Free Parameters 	&	 Value \\ 
\hline \hline 
$M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
$\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
$\dot{M}_{wind}$  &	$10^{-8}~M_{\odot}yr^{-1}$\\ 
$r_{min}$ 	&	 $4 R_{WD}$\\ 
$r_{max}$ 	&	 $12 R_{WD}$ \\ 
$\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
$\gamma$ 	&	 $1$ \\ 
$v_{\infty}$ 	&	 $3v_{esc}$ \\ 
$R_v$ 	        &	 $1\times10^{11}$cm \\ 
$\alpha$ 	&	 $4$ \\
\end{tabular}
\centering
\caption{Wind geometry parameters used in the next-generation CV model.}
\label{modelb}
\end{table}

With modest changes to the kinematics of the benchmark CV model,
it is possible to produce a `next generation model' with enhanced
line emission that comes closer to reproducing the observed optical spectrum
of a Nova-like variables. The parameters for this model (imaginatively dubbed Model B)
are show in table~\ref{modelb}, and the synthetic spectrum
is shown in figure~\ref{uvoptb}. An in and out of eclipse comparison 
between the synthetic spectrum
at an angle of $80^\circ$ and the high-inclination nova-like RW Tri 
is also shown in figure~\ref{rwtricomp}.

The similarity with the observed spectrum is striking. 
Model B produces strong emission in all the Balmer lines, 
with line to continuum ratios
comparable to those in RW Tri. 
The line to continuum ratio increases during eclipse,
as one expects if the emission is produced in a disk wind, 
thereby mimicking the behaviour of SW Sex stars.
The single-peaked \ha line is produced by our models with a 
very similar width to the observed spectrum, although it is perhaps slightly more
`flat-topped' in the synthesized data.

One of the limitations of the model is that, apart 
from in H$\alpha$, the lines are in general double-peaked. 
The lack of high-resolution data in this regard makes detailed analysis difficult,
but it would appear that understanding how single-peaked 
line emission forms and the kinematics and densities required to
modify the line profile is still an open question. 
The major fallback of the next-generation model, however, lies
in the ultraviolet. To get the required emission in the optical lines
and recombination continuum the densities required are very high.
This causes a significant collisionally excited contribution
to the UV lines, meaning that the red wing of the 
resonance species such as C\textsc{iv} no longer matches the
observed profiles.

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          Conclusions and Future Work
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{document}
%% define bibstyle and other definitions
\bibliographystyle{aabib}
%% renew commands
\renewcommand{\labelitemi}{$\bullet$}
\def\py{\textsc{Python} }
\def\tar{\textsc{Tardis} }
\def\cld{\textsc{Cloudy} }
\def\civ{C~\textsc{iv} }
\def\araa{ARAA}
\def\nat{Nature}
\def\apjl{ApJ Letters}
\def\aapr{AAPR}
\def\actaa{ACTAA} 
\def\ssr{SSR}
\def\apj{ApJ}
\def\pasp{PASP}
\def\aap{A\&A}
\def\mnras{MNRAS}
\def\aj{AJ}
\def\rmxaa{RMXAA}

@@

\begin{abstract}
High-State non-magnetic Cataclysmic Variables (CVs) 
exhibit strong Hydrogen \& Helium recombination lines in their optical 
spectra. These lines can be single peaked, and may be formed 
in the same bipolar outflow that is responsible for the
blue-shifted absorption lines seen in the Ultraviolet (UV).
Here we present results obtained by incorporating a `macro-atom' treatment into
our Monte Carlo radiative transfer code, which was
originally used to synthesize the UV spectrum of a disk-dominated CV 
with a simple biconical wind. Using an identical model, we show that the wind leaves a noticeable imprint 
on the optical spectrum, producing He II 4686 and H${\alpha}$ as well as
enhanced emission in the Ly-$\alpha$ and He II $1640$ UV lines. We find that 
a boundary layer is not essential to produce significant recombination to 
He II, and if one is present we favour temperatures of $<10^5$K to avoid
overionizing the UV resonance line species such as CIV. We also conduct Zanstra method
calculations and estimate that one would infer a boundary layer temperature of around 80,000K
from our benchmark calculation, despite it not being present in the model itself. This suggests that previous calculations
done using this method are strongly dependent on both the assumed geometry and disk
spectrum.
We also note that
the presence of a boundary layer becomes more noticeable in lower accretion rate systems.
In addition, the improved treatment of recombination means that the bound-free continuum
emission is enhanced, albeit by a modest amount.
A short exploration of a 3-variable kinematic parameter space leads to models with higher densities 
that are able to produce single-peaked line emission, and also generate sufficient recombination emission
to fill in the Balmer jump photoabsorption edge.
Finally, we present a synthetic spectrum of a next generation model in and out of eclipse,
and identify the strengths and shortcomings of the model in the context of the high inclination
Nova-like variable RW Tri.
\end{abstract}

@@

Figure~\ref{spec} shows optical synthetic spectra for the benchmark 
model for 5 different sightlines. The first thing to note is that the 
model produces some lines which are strong enough to overcome
the absorption cores lines from the disk. These lines are generally double peaked, 
implying they were formed near the base of the wind where rotational velocity
can still dominate over the slowly increasing poloidal velocity. 
We also see a general trend from absorption to emission in spectral lines
with increasing inclination, as one would expect from our wind geometry.
This is expected in CVs and can be seen clearly in figure 1. Note however
that in our models the \heiiuv line does not exhibit this behaviour, which
is somewhat surprising.

A Balmer jump is present at all inclinations. This is present
in the stellar atmosphere models used to model the disk,
and is not a result of photoabsorption through the wind.
In fact, the wind has a Balmer jump in emission, but it is not prominent enough
to overcome the intrinsic absorption in the illuminating spectrum. 
Figure~\ref{cont} shows the total escaping spectrum, integrated
over all viewing angles, with the contribution from the disk and wind
also plotted. It shows that the lines are produced in the wind,
and also that the wind is producing a Balmer recombination
continuum, but one which is not yet sufficient to mask the absorption 
intrinsic to the disk SED. This offers a tantalising hint
that modest changes to the kinematics of the wind
may be sufficient to boost the continuum emission of the wind.
Furthermore, it confirms our suspicions that the improved
radiative transfer would cause enhanced recombination emission,
suggesting that, where possible, up to date treatments of
NLTE line transfer should be used in codes such as this.
The prominent P-Cygni profiles in e.g., C\textsc{iv} are still seen
in the UV spectra (see figure~\ref{spec}). In addition, the wind 
now contributes significant Lyman-$\alpha$ and
He~\textsc{ii}~$\lambda1640{\rm \AA}$  emission. 
% We note that the ionization state of the wind 
% is such that recombination to He~\textsc{ii} is significant, even
% without a boundary layer as a source of higher energy photons.

@@

\begin{figure} 
\includegraphics[width=0.5\textwidth]{figures/fig7_escaping.eps}
\caption{Total packet-binned spectra across all viewing angles. 
The thick black line shows the total 
integrated escaping spectrum, while green and red lines show the contributions from photons that originate
in the disk and wind respectively. Recombination continuum emission blueward of the Balmer 
edge is already prominent relative to other wind continuum processes, but is not sufficient
to fill in the Balmer jump in this specific model}
\label{cont}
\end{figure}

@@

% {\bf
% \noindent key points here:

% \begin{itemize}
% 	\item producing single peaked line profiles is difficult to say the least
% 	\item with our high density models we can produce some single peaked line emission,
% 	mostly in Halpha and beta. the other lines seem to stay double peaked.
% 	\item this higher density causes (too much) collisionally excited line emission from CIV
% 	\item if the wind was more equatorial then this might help, but this isn't really supported by observations.
% 	\item we can definitely reproduce the behaviour predicted by Murray and Chiang
% 	\item Comment on the observed Balmer decrement being fairly flat, as is observed. Point out that
% 	this is necessary if H alpha is to be single peaked, as you need significant optical depths.
% 	\item \la needs to be discussed somewhere- potentially here. Personally I would like to point out
% 	that recombination being important here suggests that it might also be in QSOs
% \end{itemize}
% }

Figure~\ref{halpha} shows how the H$\alpha$ and H$\beta$ lines change with the kinematics 
of the wind at an inclination of $80^\circ$. For H$\alpha$, in models with lower densities, the
line is double peaked, but we see a transition to a single peaked line when 
a high enough density is reach such that the line becomes optically thick.
This reproduces the behaviour predicted by \cite{MC96}, who suggested that
the poloidal velocity gradient in the wind can be larger than the gradient of 
the Keplerian velocity. This velocity gradient can therefore modify the line profile shape
by suppressing emission at the red and blue wings of the line, 
providing that the line optical depth is high enough.

In order to produce single-peaked line emission at high inclinations,
it is clear that a higher line opacity is needed at the red and blue wings relative to
the opacity at line centre. This can be achieved in a number of ways. A more equatorial 
wind would increase the radial velocity shear, but is not supported by observations (references 
on collimated nature of CV winds).
Our difficulty in producing single-peaked line emission from a full 
radiative transfer calculation has been encountered before in a number of situations. 
SDL05 found that a biconical disk geometry similar to that adopted here could not reproduce 
the observed single peaked profiles in YSOs. We have shown
that the mechanism proposed by \cite{MC96} does indeed produce 
single-peaked line emission in our models, but for this to occur in the majority of
spectral lines then very high densities are required.

\begin{figure} %fullpage
\mbox{
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_alpha_0.eps}}
\quad
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_beta_0.eps}}   
}
\caption{
Line profiles for \ha\ (right) and \hb\ (left) with varying kinematic 
properties. The benchmark model is shown in the top panel, and also in grey in each 
subsequent plot for comparison. The parameter that has been altered from the benchmark model 
is marked on each panel. For the left and middle right columns, models lower down
are more slowly accelerating and have denser wind bases. The middle right column
shows the variation with wider launch radii, and the right hand column shows 
how a boundary layer of increasing temperature affects the spectrum.
% How the H$\alpha$ and H$\beta$ lines in our model change with the kinematic properties
% of the wind. The three separate panels show three different values of $\dot{M}_W$, 
% while $\alpha$ and $R_v$ are all gradually increased from top to bottom and left to right respectively.
% Larger values of these quantities increase the density at the base of the wind. There is a clear transition
% from double peaked to single peaked behaviour, and at the highest densities the wind
% essentially becomes neutral as the optically thick regions self-shield the wind from photoionizing radiation.
% \bf{Each of these figures will highlight the next gen model in bold.
% and contain a grid like the above showing a pair of spectral features in
% the left and right panels. The grey shaded line will show the benchmark model
% for easy comparison.  
% The most promising parameters at the moment are acceleration exponent and launch radii.}
% }
}
\label{halpha}
\end{figure} %fullpage

@@

The left panel of figure~\ref{jump} shows the evolution
of the Balmer jump with a number of key parameters. Higher density models
produce sufficient recombination continuum emission to fill 
in the Balmer jump. This offers a potential solution to a 
longstanding problem when reconciling theoretical
models of NL spectra with observations, as originally suggested by
\cite{KLWB98}. The fact that this emission is very sensitive to the parameters
that govern the density at the wind base also supports
the idea that a transition region close to the disk plane is necessary
to explain the emission features present \citep{kd1997}.

% {\bf
% \noindent key points here:

% \begin{itemize}
% 	\item there is always recombination continuum emission from the wind, but it
% 	only because significant w.r.t disk when the wind accelerates more slowly.
% 	\item This higher density causes (too much) collisionally excited line emission from CIV
% 	\item supports findings from the line profile shapes conclusions above...suggests
% 	we need to alter the geometry in some respect, or find someway to suppress
% 	collisionally excited line emission from UV lines?
% 	\item perhaps one should increase the volume of the emitting area rather than the density,
% 	although this will also cause more thermal line emission...
% 	\item Bottom lines: filling in the Balmer jump can be done, and at the very minimum recombination
% 	emission from the wind can matter, especially if we believe that the lines come from the wind. 
% 	But to properly fill in the edge, one requires very high, possibly unrealistic, densities.
% 	\item make clear that the edge originally comes from the stellar atmosphere, and that
% 	the model we have used here is perhaps a little pessimistic.
% 	\item We predict that the Balmer jump becomes deeper relative to the continuum 
% 	\item This is probably due to foreshortening of the disk continuum but a fairly constant
% 	escaping Balmer continuum.
% \end{itemize}
% }

\begin{figure} %fullpage
\mbox{
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_1640_0.eps}}
\quad
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_4686_0.eps}}   
}
%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
\caption{
Line profiles for \heiiuv\ (right) and \heiiopt\  (left) with varying kinematic 
properties, computed for an incliantion of $80^\circ$. 
The panels are organised in the same way as figure~\ref{halpha}.
% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
% when the wind becomes a neutral absorbing column.
}
\label{heiifig}
\end{figure}

@@

% fwoud

@@

% {\bf 
% \noindent key points here:

% \begin{itemize}
% 	\item we don't necessarily need a Boundary layer to ionize Helium II
% 	\item a Boundary layer of 200,000K overionizes Carbon IV
% 	\item we therefore favour lower boundary layer temperatures, as supported
% 	by the upper limits of Hoare and Drew 1991.
% 	\item we expect a boundary layer to matter more in lower accretion
% 	rate systems.
% \end{itemize}
% }

@@

We introduce blackbody boundary layers with temperatures of 80,000K and 200,000K,
commonly proposed values in the literature, and adopt a scale height according to
equation~\ref{bl}. We find that the strength of the C\textsc{iv} line decreases
with increasing boundary layer temperature, as shown in figure~\ref{jump}.
We note that a model boundary layer could produce a softer
spectrum for a given effective temperature \citep[e.g.][]{suleimanov2014}, 
meaning that our ionization constraints would
allow for a higher value of $T_{bl}$. It is also
possible that a flatter temperature profile in the disk,
as suggested by some eclipse mapping observations of NLs (References),
would cause a softer disk spectrum and allow a boundary layer 
with $T_{bl} = 200,000$K to exist without over-ionizing the wind.

@@

Here f(line) is the line flux in erg~cm$^{-2}$ s$^{-1}$. (I NEED TO DO THE CALCULATION!).

@@

\begin{figure} %fullpage
\mbox{
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_balmer_0.eps}}
\quad
\subfigure{\includegraphics[width=0.5\textwidth]{figures/grid_uv_0.eps}}   
}
%%\includegraphics[width=0.5\textwidth]{figures/test.eps}
\caption{The evolution of the Balmer jump and higher order Balmer lines (left) 
and the \civ\ line profile (right)
with the kinematic properties of the wind,
computed for an incliantion of $80^\circ$. 
the panels are organised in the same way as figure~\ref{halpha}.
% The panels are ordered in the same way as figure~\ref{halpha}. In general, increasing densities
% lead to a Balmer jump in emission, although as in the case of H$\alpha$ there is a transition
% when the wind becomes a neutral absorbing column.
}
\label{jump}
\end{figure}

@@

@@

\begin{table}
\centering
\begin{tabular}{p{3cm}p{4cm}}
Model B \\
\hline Free Parameters 	&	 Value \\ 
\hline \hline 
$M_{WD}$ 	 &	 $0.8 M_{\odot}$ \\ 
$\dot{M}_{acc}$ 	 &	 $10^{-9}~M_{\odot}yr^{-1}$\\ 
$\dot{M}_{wind}$  &	$10^{-8}~M_{\odot}yr^{-1}$\\ 
$r_{min}$ 	&	 $4 R_{WD}$\\ 
$r_{max}$ 	&	 $12 R_{WD}$ \\ 
$\theta_{min}$ 	&	 $20.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $65.0^{\circ}$ \\ 
$\gamma$ 	&	 $1$ \\ 
$v_{\infty}$ 	&	 $3v_{esc}$ \\ 
$R_v$ 	        &	 $142.9 R_{WD}$ \\ 
$\alpha$ 	&	 $4$ \\
\end{tabular}
\centering
\caption{Wind geometry parameters used in the next-generation CV model.}
\label{modelb}
\end{table}

With modest changes to the kinematics of the benchmark CV model,
it is possible to produce a `next generation model' with enhanced
line emission that comes closer to reproducing the observed optical spectrum
of a Nova-like variables. The parameters for this model (imaginatively dubbed Model B)
are show in table~\ref{modelb}, and the synthetic spectrum
is shown in figure~\ref{uvoptb}. An in and out of eclipse comparison 
between the synthetic spectrum
at an angle of $80^\circ$ and the high-inclination nova-like RW Tri 
is also shown in figure~\ref{rwtricomp}. The inclination
for RW Tri has been disputed, with claimed values of $75^\circ$ \citep{groot2004},
$70.5^\circ$ \citep{smak1995}, $80^\circ$ \citep{longmore1981} and 
$82^\circ$\citep{frankking1981}. A lower inclination
would mean that our model would simply require lower densities 
and smaller emission regions to produce the required continuum level
and single peaked emission, so our conclusions from this comparison are
not particular sensitive to the value chosen.
We also emphasize that this is no sense a fit to the data. The model
is designed to reproduce the general behaviour of Nova-likes
and give an indication of the likely densities and kinematics 
required in the wind, but we do not seek to provide robust parameter
or precise parameters.
%quotes a figure of , whereas  halevinhenden2008

The similarity with the observed spectrum is striking. 
Model B produces strong emission in all the Balmer lines, 
with line to continuum ratios
comparable to those in RW Tri. 
The line to continuum ratio increases during eclipse,
as one expects if the emission is produced in a disk wind, 
thereby mimicking the behaviour of SW Sex stars.
The single-peaked \ha\ line is produced by our models with a 
very similar width to the observed spectrum, although it is perhaps slightly more
`flat-topped' in the synthesized data.

One of the limitations of the model is that, apart 
from in H$\alpha$, the lines are in general double-peaked. 
The lack of high-resolution data in this regard makes detailed analysis difficult,
but it would appear that understanding how single-peaked 
line emission forms and the kinematics and densities required to
modify the line profile is still an open question. 
The major fallback of the next-generation model, however, lies
in the ultraviolet. To get the required emission in the optical lines
and recombination continuum the densities required are very high 
($n_e\sim10^{13}-10^{14}$ in the main emission region).
This causes a significant collisionally excited contribution
to the UV lines, meaning that the red wing of the 
resonance species such as C\textsc{iv} no longer matches the
observed profiles.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%          Conclusions and Future Work
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
